---
title          : "Opening open science to all: Demystifying reproducibility and transparency practices in linguistic research"
authors        : "Joseph V. Casillas, Gabriela Constantin-Dureci, Iván Rascón Andreu, Jiawei Shao, Stephanie A. Rodríguez, Adrija Gadamsetty, Alexandria Minetti, Krishita Laungani, John Thatcher, Rhode-Taina Gardere, Katherine Taveras, Isabelle Chang, Nicole Rodríguez, Meritxell Feliu Ribas & Kyle Parrish"
journal        : "Linguistics: An Interdisciplinary Journal of the Language Sciences"
manuscript-id  : "LING.2023.0249"
manuscript-src : "headings"

header-includes:
  - \usepackage{tipa}
  - \usepackage{booktabs}
  - \usepackage{hyperref}
  - \usepackage{longtable}
  - \usepackage{array}

bibliography      : "../../../bib/os_refs.bib"
csl               : "../../../bib/apa-6th-edition.csl"

cutout-quotes  : false
class          : "final"
output         : papaja::revision_letter_pdf
---

```{r}
#| label: setup
library("here")
```


Dear Dr. Volker Gast, 

Thank you for taking the time to consider our manuscript _`r rmarkdown::metadata$title`_ (`r rmarkdown::metadata$manuscript`) for publication in _`r rmarkdown::metadata$journal`_. 
Our understanding is that we needed to consider the reviewers' comments and revise accordingly before the manuscript could be reevaluated for publication. 
We noted X specific areas that were consistently highlighted by the reviewers as needing improvement: x, y, and z. 
We have considered thoroughly the detailed feedback provided by all three reviewers and resubmit what we believe to be a much improved version of the manuscript. 
In this letter we address the reviewers' concerns point-by-point. 
Where feasible, we quote all revised text in this document, otherwise, we refer the reader to the relevant sections of the revised manuscript. 
We thank you and the three anonymous reviewers for all comments and suggestions and again enthusiastically submit the revised manuscript for consideration in _`r rmarkdown::metadata$journal`_.


Sincerely,  
Joseph Casillas  
(corresponding author)

\clearpage

# Reviewer \#1

```{r}
#| child: "reviewer_1.Rmd"
#| eval: TRUE
```

\clearpage

# Reviewer \#2

```{r}
#| child: "reviewer_2.Rmd"
#| eval: TRUE
```

\clearpage

# Reviewer \#3

```{r}
#| child: "reviewer_3.Rmd"
#| eval: TRUE
```

\newpage

# References {-}

::: {#refs custom-style="Bibliography"}
:::
